Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-08 ccppabc/text/revision/main.tex
Edits on Figure captions for 7,8, 9, 10

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABC vs MCMC Histograms 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_nbarxi.pdf}
\caption{\label{fig:hist_nbarxi} 
{\bf \color{dred}
We compare the $\log \mathcal{M}_{\rm min}$, $\alpha$, and $\log \mathcal{M}_{1}$ parameter 
constraints from ABC-PMC (orange) to constraints from the Gaussian pseudo-ikelihood MCMC (blue) 
using $\ngalaxy$ and $\xigg(r)$ as observables. The \emph{top} panels compares the two methods' 
marginalized posterior PDFs over the parameters. In the \emph{bottom} panels, we include box 
plots marking the confidence intervals of the posterior distributions. The boxes represent the 
$68\%$ confidence interval while the ``whiskers'' represent the $95\%$ confidence interval. We mark 
the ``true'' HOD parameters with vertical black dashed line. The marginalized posterior PDFs 
}
obtained from the two methods are consistent with each other. The ABC-PMC constraints are slightly 
narrower for $\log \mathcal{M}_{\rm min}$, slightly wider for $\log \mathcal{M}_{1}$, and slightly 
less biased for $\alpha$.} 
%\end{center}
\end{figure*}

\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_nbargmf.pdf}
\caption{\label{fig:hist_nbargmf} Same as Figure \ref{fig:hist_nbarxi}, but both the ABC-PMC analysis and the standard Gaussian 
Likelihood MCMC analysis are done using the observables $\ngalaxy$ and $\gmf(N)$. The constraints are 
consistent with the ``true'' HOD parameters and both methods infer the region of allowed values to similar 
precision. The MCMC result for $\alpha$ is slightly more biased compared to ABC-PMC estimate. 
This may stem from the fact that the use of Gaussian-likelihood and its associated assumptions is more 
spurious when modeling the group multiplicity function.}
%\end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABC vs MCMC Contours nbar +xi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_contour_nbarxi.pdf}
\caption{\label{fig:cont_nbarxi}
 We compare the ABC-PMC (orange) and the Gaussian likelihood MCMC (blue)
predictions of the 68\% and 95\% posterior confidence regions over the HOD 
parameters ($\log \mathcal{M}_{\rm min}$, $\alpha$, and $\log \mathcal{M}_{1}$) 
using $\ngalaxy$ and $\xigg(r)$ as observables. The ``true'' HOD parameters used 
to create the mock observations are plotted by black stars in each panel. The two approaches are consistent with the true values of the parameters used to generate the data.}
%\end{center}
\end{figure*}

\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_contour_nbargmf.pdf}
\caption{ \label{fig:cont_nbargmf} Same as Figure \ref{fig:cont_nbarxi}, but using $\ngalaxy$ and $\gmf(N)$ as observables. Again, both methods accurately estimate the parameter value regions of the true values for the data. The MCMC estimation of $\alpha$ by use of a Gaussian-likelihood is biased when compared with the ABC-PMC contours. This may be due to the fact that the group multiplicity function is particularly unsuited to the use of a Gaussian-likelihood analysis.}
%\end{center}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABC vs MCMC Histograms 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_nbarxi.pdf}
\caption{\label{fig:hist_nbarxi} 
{\bf \color{dred}
We compare the $\log \mathcal{M}_{\rm min}$, $\alpha$, and $\log \mathcal{M}_{1}$ parameter 
constraints from ABC-PMC (orange) to constraints from the Gaussian pseudo-ikelihood MCMC (blue) 
using $\ngalaxy$ and $\xigg(r)$ as observables. The \emph{top} panels compares the two methods' 
marginalized posterior PDFs over the parameters. In the \emph{bottom} panels, we include box 
plots marking the confidence intervals of the posterior distributions. The boxes represent the 
$68\%$ confidence interval while the ``whiskers'' represent the $95\%$ confidence interval. We mark 
the ``true'' HOD parameters with vertical black dashed line. The marginalized posterior PDFs 
obtained from the two methods are consistent with each other. The ABC-PMC and Gaussian pseudo-likelihood
constraints are generally consistent for $\log \mathcal{M}_{\rm min}$ and $\log \mathcal{M}_{1}$. 
The ABC-PMC constraint for $\alpha$ is slightly less biased and has slightly larger uncertainty
then the constraint from Gaussian pseudo-likelihood analysis.} 
}
%\end{center}
\end{figure*}

\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_nbargmf.pdf}
\caption{\label{fig:hist_nbargmf} 
{\bf \color{dred}
Same as Figure \ref{fig:hist_nbarxi}, but both the ABC-PMC
analysis and the Gaussian pseudo-likelihood MCMC analysis use $\ngalaxy$ and $\gmf(N)$ as 
observables. Both methods derive constraints consistent with the ``true'' HOD parameters 
and infer the region of allowed values to similar precision. We note that the MCMC constraint 
on $\alpha$ is slightly more biased compared to ABC-PMC estimate. This discrepancy may stem 
from the fact that the use of Gaussian pseudo-likelihood and its associated assumptions is more 
spurious when modeling the group multiplicity function.}
}
%\end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABC vs MCMC Contours nbar +xi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_contour_nbarxi.pdf}
\caption{\label{fig:cont_nbarxi}
{\bf \color{dred}
We compare the ABC-PMC (orange) and the Gaussian pseudo-likelihood MCMC (blue)
predictions of the 68\% and 95\% posterior confidence regions over the HOD 
parameters ($\log \mathcal{M}_{\rm min}$, $\alpha$, and $\log \mathcal{M}_{1}$) 
using $\ngalaxy$ and $\xigg(r)$ as observables. In each panel, the black star
represents the ``true'' HOD parameters used to generate the mock observations. 
Both inference methods derive confidence regions consistent with the ``true'' 
HOD parameters.
}
}
%\end{center}
\end{figure*}

\begin{figure*}
%\begin{center}
\includegraphics[width=1.\textwidth]{figs/paper_ABCvsMCMC_contour_nbargmf.pdf}
\caption{ \label{fig:cont_nbargmf} 
Same as Figure \ref{fig:cont_nbarxi}, but using $\ngalaxy$ and $\gmf(N)$ as 
observables. Again, the confidence regions derived from both methods are 
consistent with the ``true'' HOD parameters used to generate the mock 
observations. The confidence region of $\alpha$ from the Gaussian 
pseudo-likelood method is biased compared to the ABC-PMC contours. 
This may be due to the fact that the true likelihood function that 
describes $\gmf(N)$ deviates significantly from the assumed Gaussian 
functional form.}
}
%\end{center}
\end{figure*}
